\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-22 tex/paper.tex
Added tech stack figure
Changed to description for related tech

\subsection{Related Technologies}
\subsubsection{React} \label{sec:react}
React is a JavaScript library for building user interfaces. React uses both its own virtual DOM and
the browser's normal DOM, this makes it able to efficiently update dynamic web pages after a change
of state through comparing the old virtual DOM with the resulting virtual DOM after the state change
and then only update the browser's DOM according to the delta between the virtual DOMs~\cite{REACT}.
React can be seen as the system for handling views in front-ends implementing a MVC-like
(Model-View-Controller) architecture. In this work React is used as a part of building the
front-end.

\subsubsection{Reflux} \label{sec:reflux}
Reflux~\cite{REFLUX} is an idea and a simple library of how to structure your application. It
features a unidirectional dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than
for example Flux~\cite{FLUX}, when using a functional reactive programming style. Reflux is used
together with React (see Section~\ref{sec:react}) for this implementation to define a structure of
the flow of data and state changes.

@@

\subsubsection{Scala} \label{sec:scala}
Scala is a multi-paradigm programming language. It most commonly runs on the JVM and unlike
Java it supports most functional programming features at the same time as it supports 
object-oriented programming~\cite{SCALA}. Scala is used to program the back-end and the Spray
toolkit (see Section~\ref{sec:spray}) is used with it to simplify the API.

\subsubsection{REST} \label{sec:rest}
REST stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.

\subsubsection{Spray} \label{sec:spray}
Spray~\cite{CASBAH} is an open-source toolkit written in Scala and for Scala (see
section~\ref{sec:scala}). It is used to make it easier to build REST/HTTP APIs (see
section~\ref{sec:rest}) and those abilities is what it is used in the implementation (see
section~\ref{sec:api}).

\subsubsection{MongoDB} \label{sec:spray}
MongoDB is a document-oriented database, which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks the support for joins to
improve its possibility to scale, which can be a big downside to some applications containing the
need for such logic. MongoDB is used as a persistent storage for the back-end to store all the
projects and nodes in the tree structures and also the files uploaded to the system. Scala (see
Section~\ref{sec:scala}) uses a layer called Casbah~\cite{CASBAH} to interface with MongoDB.

\subsection{Methods for determining\\implementation details}
This chapter introduces the different methods used to determine how the new system should be
implemented, which persistent storage it should use and how the estimation of long-term scaling 
was done.
\\
\par As this work was not mainly about the system architecture, but rather about evaluating the
effects of using Copy-on-Write, the decisions taken for the different technologies used were simply
made from what the author was comfortable with and knew would have little impact on the evaluation. 
With that said there are no comparisons of for example different databases, protocols or API
solutions in this paper.

>>>>

\subsection{Architecture and Technologies used}

\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.8]{techstack.pdf}
    }
    \caption{Technology Stack}
    \label{fig:tech_stack}
\end{figure}

\begin{description}
\item[React]% \hfill \\ % \label{sec:react}
is a JavaScript library for building user interfaces. React uses both its own virtual DOM and
the browser's normal DOM, this makes it able to efficiently update dynamic web pages after a change
of state through comparing the old virtual DOM with the resulting virtual DOM after the state change
and then only update the browser's DOM according to the delta between the virtual DOMs~\cite{REACT}.
React can be seen as the system for handling views in front-ends implementing a MVC-like
(Model-View-Controller) architecture. In this work React is used as a part of building the
front-end.

% \hfill \\ % \label{sec:reflux}
\item[Reflux]~\cite{REFLUX} 
is an idea and a simple library of how to structure your application. It features a unidirectional
dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than for example
Flux~\cite{FLUX}, when using a functional reactive programming style. Reflux is used together with
React for this implementation to define a structure of the flow of data and state changes.

@@

\item[Scala]% \hfill \\ %\label{sec:scala}
is a multi-paradigm programming language. It most commonly runs on the JVM and unlike Java it
supports most functional programming features at the same time as it supports object-oriented
programming~\cite{SCALA}. Scala is used to program the back-end and the Spray toolkit is used with
it to simplify the API.

\item[REST]% \hfill \\ %\label{sec:rest}
stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.

% \hfill \\ %\label{sec:spray}
\item[Spray]~\cite{CASBAH} % Spray in casbah book
is an open-source toolkit written in Scala and for Scala. It is used to make it easier to build
REST/HTTP APIs and those abilities is what it is used in the implementation.

\item[MongoDB]% \hfill \\ %\label{sec:spray}
is a document-oriented database, which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks the support for joins to
improve its possibility to scale, which can be a big downside to some applications containing the
need for such logic. MongoDB is used as a persistent storage for the back-end to store all the
projects and nodes in the tree structures and also the files uploaded to the system. Scala uses a
layer called Casbah~\cite{CASBAH} to interface with MongoDB.

\end{description}
\subsection{Methods for determining\\implementation details}
This chapter introduces the different methods used to determine how the new system should be
implemented, which persistent storage it should use and how the estimation of long-term scaling 
was done.
\\
\par As this work was not mainly about the system architecture, but rather about evaluating the
effects of using Copy-on-Write, the decisions taken for the different technologies used were simply
made from what the author was comfortable with and knew would have little impact on the evaluation. 
With that said there are no comparisons of for example different databases, protocols or API
solutions in this paper.
